\chapter{Benchmark}

\section{Available MRI benchmarks}

\subsection{OpenNeuro: FCDTypeII}
\label{dt:benchmark8}

Here: \href{https://openneuro.org/datasets/ds004199/versions/1.0.6}{An open presurgery MRI dataset of people with epilepsy and focal cortical dysplasia type II}

85 controls and 85 patients composed of FLAIR and T1w images, with full details about the MRI and the patient (anonymous but sex, age at scan)

\subsection{EPISURG}

Benchmark available here: \href{https://torchio.readthedocs.io/_modules/torchio/datasets/episurg.html#EPISURG}{torchio.readthedocs.io/EPISURG}

Real link is here: \href{https://rdr.ucl.ac.uk/articles/dataset/EPISURG_a_dataset_of_postoperative_magnetic_resonance_images_MRI_for_quantitative_analysis_of_resection_neurosurgery_for_refractory_epilepsy/9996158/1?file=26153588}{EPISURG article link}
However, it doesn't work properly on Firefox for now.

This is composed of 430 postoperative MRI. The corresponding preoperative MRI is present for 268 subjects.

The dataset is 5.4 GB.

Have to cite the paper if used.

\subsection{IXI Dataset}

Here:\href{https://brain-development.org/ixi-dataset/}{database link}

600 MR images from healthy subjects. Containing T1, T2, PD-weighted images ; MRA images, Diffusion-weighted images.

From three different hospitals

1.5T and 3T MRIs

\subsection{PLoSONE\_MRI\_CAD\_paper}
\label{dt:ul3}

Even though there are two links, they refer to the same thing. Just in case, they are both here anyway.

\href{https://figshare.com/articles/journal_contribution/PLoSONE_MRI_CAD_paper/3573471?file=5653479}{public benchmark link}

\href{https://figshare.com/s/70178bc154bd83258322?file=5653479}{private benchmark link}

\subsection{Zenodo DeepFCD}
\label{dt:res18}

From \citeref{res18}

148 FCD patients with T1 and FLAIR MRI

Here: \href{https://zenodo.org/records/7844202}{benchmark link}

\section{On-demand MRI Benchmarks}

\subsection{ADHD200-Sample}

\href{https://fcon_1000.projects.nitrc.org/indi/adhd200/}{benchmark link}

Used in article in \ref{res1}

\subsection{MELD Project}

The database is accessible on demand here: \href{https://meldproject.github.io//}{website}

The GitHub is here in \citeref{code:res2}

The research is here in \citeref{res2}

\subsection{3D CNN data}

Article here: \citeref{res7}

Data available on demand to the author.

\subsection{Human connectome}

Benchmark available here: \href{https://www.humanconnectome.org/study/hcp-young-adult}{benchmark link}

\subsection{Sree Chitra Tirunal Institute for Medical Sciences and Technology}

Benchmark surely available on demand


\subsection{FastMRI}
\label{dt:FastMRI}

Here: \href{https://fastmri.med.nyu.edu/}{direct link}

PapersWithCode here: \href{https://paperswithcode.com/dataset/fastmri}{paperswithcode link}

To access to the data, need to ask the owner.

Contains MRI of knees, brains, breasts and prostates. Repartition here: \citeref{tab:FastMRI}

\begin{table}[htbp]
	\centering
	\fbox{
	\begin{tabular}{l l l l}
		\textbf{Field Strength} & \textbf{1.5T} & \textbf{3T} & \\
		T1 & 382 & 409 & \\
		T1 post contrast & 849 & 646 & \\
		T2 & 1655 & 2524 & \\
		FLAIR & 126 & 411 & \\
		Total & 3012 & 3990 & 7002 \\
	\end{tabular}
	}
	\caption{Repartition in the benchmark of FastMRI (\citeref{dt:FastMRI})}
	\label{tab:FastMRI}
\end{table}

\subsection{Brain Tumor MRI Dataset}

PapersWithCode here: \href{https://paperswithcode.com/dataset/brain-tumor-mri-dataset}{paperswithcode link}

This contains nothing for epilepsy, but contains "regular" brains MRI

\subsection{Br35H::Brain Tumor Detection 2020}
\label{dt:br35h}

PapersWithCode here: \href{https://paperswithcode.com/dataset/br35h-brain-tumor-detection-2020}{paperswithcode link}

Kaggle here: \href{https://www.kaggle.com/datasets/ahmedhamada0/brain-tumor-detection}{kaggle link}

Contains 3000 MRI images of brains, both tumorous or not. Can be used for control images.

Condition of gathering not given.

Repartition here: \citeref{tab:br35h}

\begin{table}[htbp]
	\centering
	\fbox{
	\begin{tabular}{l l l}
		\textbf{Folder name} & \textbf{Amount} & \textbf{Description} \\
		Yes & 1500 & Brain is tumorous \\
		No & 1500 & Brain isn't tumorous \\
		Pred & 3060 & No idea \\
		Total & 3000 & \\
	\end{tabular}
	}
	\caption{Repartition in the benchmark of Br35H (\citeref{dt:br35h})}
	\label{tab:br35h}
\end{table}

\subsection{AOMIC (Amsterdam Open MRI Collection)}
\label{dt:aomic}

PapersWithCode here: \href{https://paperswithcode.com/dataset/aomic}{paperswithcode link}

AOMIC website here: \href{https://nilab-uva.github.io/AOMIC.github.io/}{website link}

Paper explaining the data: \href{https://www.nature.com/articles/s41597-021-00870-6}{paper link}

Lots of images here, mainly usable for controls. Shouldn't be epileptic MRI here.

Repartition here: \citeref{tab:aomic}


\begin{table}[htbp]
	\centering
	\fbox{
	\begin{tabular}{l l}
		\textbf{Origin} & \textbf{Amount} \\
		T1-weighted & 928 \\
		No & 1500 \\
		Pred & 3060 \\
		Total & 3000 \\
	\end{tabular}
	}
	\caption{Repartition in the benchmark of AOMIC (\citeref{dt:aomic})}
	\label{tab:aomic}
\end{table}

\subsection{Alzheimer's Disease Neuroimaging Initiative}

On demand, contains lots of things

Here: \href{https://adni.loni.usc.edu/}{link here}

\section{Other benchmarks}

\subsection{EEG}

Benchmark here: \href{https://paperswithcode.com/dataset/epilepsy-seizure-prediction}{paperswithcode link}

\section{Tools}

\subsection{TorchIO}

GitHub here: \href{https://github.com/TorchIO-project/torchio}{github link}

PapersWithCode here: \href{https://paperswithcode.com/paper/torchio-a-python-library-for-efficient}{paperswithcode link}
